---
title: "Impeachment Data 2020"
description: |
 This post is showing specific data from the first Trump impeachment in 2020.
author:
  - name: Nicole Miller
    url: https://www.google.com
date: 04-18-2021
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

I began by loading the necessary libraries and downloading the data frame called 'impeach' which contained data with all House Democrats and election results/demographics. This data also indicated whether or not a member publicly called for impeachment.

```{r}
library(tidyverse)
library(lubridate)

impeach <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vRh8d5JaDqBtByzNw2JZF3idaACobDhhk-p7chJoktA0HawELHFOvjQOqCpzGA4MGONvPlR7GASqW-K/pub?gid=1765341510&single=true&output=csv")

```

Once the data frame was imported, I filtered the data in many different ways. I will only be showing a few examples below.

One of the first things I did was filter the data to return only results where a member is both against impeachment, and comes from a district that President Trump won in 2016.

**You can see the results from the code below:**

```{r}
impeach %>%
  filter(for_impeachment == "NO", p16winningparty == "R") %>%
  select(for_impeachment, first_name, last_name, p16winningparty)

```
Another way I filtered the data was to only show results from September 2019 where a member voted YES for impeachment.

**This is shown below:**

```{r}
impeach%>%
  filter(date_month == "9", date_year == "2019", for_impeachment == "YES") %>%
  select(for_impeachment, first_name, last_name, date_exact)

```

In addition to filtering, I also sorted the entire data frame based on who voted NO for impeachment based on the percentage of a district that has a bachelor's degree or higher, from lowest to highest.

**This is shown below:**

```{r}
impeach%>%
  filter(for_impeachment == "NO") %>%
  arrange(pct_bachelors) %>%
  select(for_impeachment, pct_bachelors)

```
The final thing I will show from this data set will involve grouping. Below is the code that will show the combined MEAN/AVERAGE percentage of college grads for all districts that are Yes for impeachment vs. No.

**Shown below:**

```{r}
impeach%>%
  group_by(for_impeachment) %>%
  summarise(pct_bachelors = mean(pct_bachelors)) %>%
  arrange(desc(pct_bachelors))
```

Those are just some examples of different ways you can filter, sort, and group the 'impeach' data frame linked above. The possibilities are endless!

